### 2021-07-24 ch/7-discussion.tex
Rewrite last sentence

% ======== is it fair that AI has to be fair, if humans tend to be unfair anyhow? ========
%   - yes, because there is no excuse to make something artificially biased, and also, an AI might affect many more people than a single person
%   - it's like asking: isn't it unfair that our president should have a better character than the average person?
It was mentioned before that an \ac{ML} model should be judged by how useful it is,
how it stacks up to realistic alternatives, and not if it is perfect.
However, one has to be careful not to take this philosophy too far.
Namely, one should avoid giving up and saying,
``why should AI need to be fair if humans tend to be bias anyhow?''
The faults of humans has little to do with the question of what we expect of machines.
% and we should certainly not go out of our way to encode the same biases in our creations.
If one of our machines will affect many of our fellow humans,
we would not want it to be harmful, right?
Should we make the machine artificially biased
so that humans do not need to feel too guilty about their own biases?
I believe this to be folly.
We should always strive to do the best we can,
even if this leads to a world in which machines are less biased than humans.
% ==============

>>>>

% ======== is it fair that AI has to be fair, if humans tend to be unfair anyhow? ========
%   - yes, because there is no excuse to make something artificially biased, and also, an AI might affect many more people than a single person
%   - it's like asking: isn't it unfair that our president should have a better character than the average person?
It was mentioned before that an \ac{ML} model should be judged by how useful it is,
how it stacks up to realistic alternatives, and not if it is perfect.
However, one has to be careful not to take this philosophy too far.
Namely, one should avoid giving up and saying,
``why should AI need to be fair if humans tend to be bias anyhow?''
The faults of humans has little to do with the question of what we expect of machines.
% and we should certainly not go out of our way to encode the same biases in our creations.
If one of our machines will affect many of our fellow humans,
then I think we would not want it to be harmful.
Should we make the machine artificially biased
so that humans do not need to feel too guilty about their own biases?
I believe this to be folly.
We should always strive to do the best we can
and that means making machines as unbiased as possible.
% ==============
